\documentclass{res} 			% LaTeX resume using res.cls
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage[none]{hyphenat}		% no hyphenation patterns exist
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  			% use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}FirstName LastName} % force lhead all the way left
\rhead{Page \thepage}  			% put page number at right
\cfoot{}  						% the footer is empty
\pagestyle{fancy} 				% set pagestyle for the document
\setmainfont{Palatino Linotype} % set custom font

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{FirstName LastName\ {\fontspec{KaiTi} (姓名)}}
\address{ \vspace{0.2in} \\
  Room 123, XXX Building, \\
  No. 88 XXX Street,\\
  Hong Kong, China} 
\address{ \vspace{0.2in} \\
  Tel: +852 1234 5678 \\
  Email: name@domain.com \\
  http://domain.com \\}

\begin{resume} 
\vspace{0.1in}

\section{RESEARCH INTERESTS}
\vspace{0.1in}
	XXXX, XXXX


\section{EDUCATION}
\vspace{0.1in} 
    {\bf ABC University}, Hong Kong \\
    {\sl Ph.D. in XXX, Aug. 2020} \\
    Advisor: Prof. XXXX
    
    {\bf DEF University}, Hong Kong \\
    {\sl M.Sc. in XXX, 2016} 

    {\bf GHI University}, China \\
    {\sl B.A. in XXX, 2015}


\section{PROFESSIONAL EXPERIENCE} 
\vspace{0.1in} 
    {\bf Teaching Assistant}, 
    Department of XXX,
    ABC University, Hong Kong,
    Aug. 2016 - Present \\
    CourseCode: Course Name, 2017/18 \\
    CourseCode: Course Name, 2016/17 \\
    CourseCode: Course Name, 2016/17
    
    {\bf Research Assistant},
    Department of XXX,
    DEF University, Hong Kong,
    Nov. 2015 - Jun. 2016 \\
    Supervisor: Prof. XXX
    
    {\bf Summer Internship}, 
    JKL Company, Beijing, 
    Jul. 2014 - Aug. 2014 \\
    Tutor: Mr. XXX
    

\section{WORKING PAPERS} 
\vspace{0.1in}
	``{\bf Working Paper Title}'', {\sl XXX thesis}, 2015. \\
		Introduction of your working paper (if necessary).

	``{\bf Working Paper Title}'', {\sl XXX working paper}, 2016. \\
		Introduction of your working paper (if necessary).


\section{WORK IN PROGRESS}
\vspace{0.1in}
	``Title of Paper in Progress'', {\sl XXX working paper}.
	
	``Title of Paper in Progress'', {\sl XXX working paper}.


\section{PRESENTATIONS} 
\vspace{0.1in}
	XXX Conference, Apr. 2017
	
	XXX Presentations, Apr. 2016
	
	
\section{RESEARCH GRANTS} 
\vspace{0.1in}
	XXX Program (Project Code), XXX Institution, 2014
	
	XXX Program (Project Code), XXX Institution, 2014
	
	
\section{SELECTED AWARDS \& RESEARCH GRANTS} 
\vspace{0.1in}
   XXX Fellowship, XXX Institution, 2016 - 2020
   
   XXX Prize, XXX Competition, 2015


\section{SKILLS \& QUALIFICATION} 
\vspace{0.1in}
   Language: Chinese Mandarin (native), English (fluent)

   Computer skills: \LaTeX, Stata, Matlab, Eviews
   
   Qualification: XXXX
   

\end{resume}

\vspace{0.5in}
\leftskip=15em Last updated: \today

\end{document}